Arrows for Parallel Computations

### 2017-12-17 paper/content/topologySkeletons.tex
minor

ptorus :: (Arrow arr, Future fut a, Future fut b) =>
	arr (c, a, b) (d, a, b) -> arr (c, fut a, fut b) (d, fut a, fut b)
ptorus f = arr (\ ~(c, a, b) -> (c, get a, get b)) >>> f >>> arr (\ ~(d, a, b) -> (d, put a, put b))
\end{code} % $
\caption{Definition of the |torus| skeleton. The definitions of |lazyzip3|, |uncurry3| and |threetotwo| have been omitted and can be found in Fig.~\ref{fig:lazyzip3etc}}.
\label{fig:torus}
\end{figure}
As an example of using this skeleton, \citet{Eden:SkeletonBookChapter02} showed the matrix multiplication using the Gentleman algorithm (\citeyear{Gentleman1978}). An adapted version can be found in Fig.~\ref{fig:torusMatMult}.
\begin{figure}[tb]
\begin{code}
type Matrix = [[Int]]

>>>>

ptorus :: (Arrow arr, Future fut a conf, Future fut b conf) =>
          conf ->
          arr (c, a, b) (d, a, b) ->
          arr (c, fut a, fut b) (d, fut a, fut b)
ptorus conf f =
	arr (\ ~(c, a, b) -> (c, get conf a, get conf b)) >>>
	f >>>
	arr (\ ~(d, a, b) -> (d, put conf a, put conf b))
\end{code} % $
\caption{Definition of the |torus| skeleton. The definitions of |lazyzip3|, |uncurry3| and |threetotwo| have been omitted and can be found in Fig.~\ref{fig:lazyzip3etc}}.
\label{fig:torus}
\end{figure}
As an example of using this skeleton, \citet{Eden:SkeletonBookChapter02} showed the matrix multiplication using the Gentleman algorithm (\citeyear{Gentleman1978}). An adapted version can be found in Fig.~\ref{fig:torusMatMult}.
\begin{figure}[tb]
\begin{code}
type Matrix = [[Int]]
